I.STRING...........
1.String --> Strings are sequence of characters written inside quotes. 
2.lower()
3.Upper()
4.Title()
5.Capitalize()
6.Find()
7.Len()
8.Count()
9.Replace()
10.ISDIGIT()
11.ISALPHA()
12.ISALNUM()
13.EndsWith()
14.Split()
15.Join()
16.Strip()
--------------------------------------------------------------------------------------------------
II.LISTS............
1.list --> list is built-in data-type that store values defferent data-type like int,float,string

2.append(): Adds an element at the end of the list.
3.extend(): Adds multiple elements to the end of the list.
4.insert(): Adds an element at a specific position.
5.clear(): removes all items.
6.POP()
7.Clear()
8.Index()
9.Count()
10.Sort()
11.Reverse()
12.Copy()
--------------------------------------------------------------------------------------------------
III.TUPLE.............
A tuple is an immutable ordered collection of elements.

Tuples are similar to lists, but unlike lists, they cannot be changed after their creation.
ordered, and immutable.

--------------------------------------------------------------------------------------------------
IV.OOPS
1.Class And Object
2.Inheritance
3.Polymorphism
4.Encapsulation
5.Data Abstraction
~Constructor
~Decorator
~Static Method
-------------------------------------------------------------------------------------------------
V.Function
Function are a Block Of Statement That Does a specific Tasks
1.without Return And Without Argument
2.without Argument and with Return 
3.with Return And With Argument

4.Function Argument
5.default Argument
6.keyword Argument
7.position Argument
8.Arbitrary Argument
9.Modules in python



